Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-04-26 paper-RMDON.tex
arreglos pequenos

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Arroyo\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica}
\thanks{\IEEEauthorrefmark{1}E-mail: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}
\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20th, 2017.}
\thanks{First draft revised on May 8th, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

@@

>>>>

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Rodríguez Arroyo\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica}
\thanks{\IEEEauthorrefmark{1}E-mail: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}
\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20th, 2017.}
\thanks{First draft revised on May 8th, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

\section{Introduction}

\section{Real-Time Scheduling Algorithms}

\subsection{On mobile devices}

\section{Scheduling algorithm 1}
\section{Scheduling algorithm 2}
\section{Scheduling algorithm 3}

\section{Conclusion}

@@

\bibitem{rao-vrudhula-daler}R.~Ravishankar, V.~Sarma and R.~Daler N, \emph{Battery modeling for energy aware system design},  Computer, IEEE Xplore Digital Library, Volume 36, Pages 77-87, 2003

\bibitem{yuan-nahrstedt}W.~Yuan and K.~Nahrstedt, \emph{Energy-efficient soft real-time CPU scheduling for mobile multimedia systems},  ACM SIGOPS Operating Systems Review, Volume 37, Pages 149-163, 2003
